%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{banking}

\moderncvcolor{black}

\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault} 
\usepackage[T1]{fontenc}

\usepackage[utf8]{inputenc}

\usepackage[left=2cm, right=2cm, top=1.7cm]{geometry}

\usepackage{import}

\name{Luke}{Pothier} 

\address{Cape Town, South Africa}

\phone[mobile]{+27 83 701 1902}

\email{lukepothier@gmail.com}

\homepage{lukepothier.com}

\begin{document}

\makecvtitle

\vspace{-20pt}

I'm a software engineer with more than six years of professional experience building bespoke mobile applications, web applications, and back-end software systems. I have experience working within and leading scrum development teams working on several projects for a wide variety of clients. In my personal capacity, I have released several open-source software projects. I have been closely involved with technical training programmes for developers.\\

\vspace{-12pt}

\section{Professional experience}

\vspace{3pt}

\begin{itemize}

\item{\cventry{November 2018 -- August 2020}{Head of Development}{Full Stack}{Cape Town, South Africa}{}{\vspace{3pt} 
\begin{itemize}
\item Leading Full Stack's development department, which comprises 20-25 developers.
\item High-level oversight of 5-10 separate projects at any given time.
\item Performing a technical leadership role on several projects concurrently.
\item Daily coding and code reviewing.
\item Management duties associated with being a member of the company's management committee.
\end{itemize}
}}

\vspace{3pt}

\item{\cventry{August 2014 -- November 2018}{Software Developer}{Full Stack}{Cape Town, South Africa}{}{\vspace{3pt}
\begin{itemize}
\item Working in small developments teams, sometimes as a technical lead.
\item Performing code review with team members.
\end{itemize}
}}

\vspace{3pt}

\item{\cventry{June 2014 -- August 2014}{Software Development Intern}{Kalahari}{Cape Town, South Africa}{}{\vspace{3pt}
\begin{itemize}
\item Working on a small front-end project in a team with other interns.
\end{itemize}
}}

\end{itemize}

\section{Education}

\vspace{3pt}

\begin{itemize}

\item{\cventry{2011 -- 2013}{Cape Town}{Bachelor of Social Sciences in Philosophy and Economic History}{University of Cape Town}{\textit{South Africa}}{}}

\end{itemize}

\vspace{2pt}

\section{Languages}

\vspace{1pt}

\begin{itemize}

\item \textbf{C\#:} Expert 

\vspace{1pt}

\item \textbf{Java:} Proficient 

\vspace{1pt}

\item \textbf{JavaScript/TypeScript:} Proficient 

\vspace{1pt}

\item \textbf{HTML/CSS:} Proficient 

\vspace{1pt}

\item \textbf{SQL:} Proficient 

\vspace{1pt}

\item \textbf{Kotlin:} Capable 

\vspace{1pt}

\item \textbf{Python:} Capable 

\end{itemize}

\section{References}

\vspace{3pt}

\begin{itemize}

\item Andrew La Grange, Managing Director, Full Stack: \href{mailto:andrew.lagrange@fullstack.co.za}{andrew.lagrange@fullstack.co.za}
\begin{itemize}
\item or see my letter of recommendation from Andrew at \href{https://lukepothier.com/files/lor.pdf}{lukepothier.com/files/lor.pdf}
\end{itemize}
\item Werner Visser, Director, Full Stack: \href{mailto:werner.visser@fullstack.co.za}{werner.visser@fullstack.co.za}
\item Herculaas van Heerden, Director, Full Stack: \href{mailto:herculaas.vanheerden@fullstack.co.za}{herculaas.vanheerden@fullstack.co.za}

\end{itemize}

\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}

\end{document}
